Numerical trajectory patterns of floating macroalgae

### 2020-11-05 thesis_chapter_3.Rmd
updated script to match new simulations

@@

Mean_KFloat_H085_W15$type <- "Mean_KFloat_H090_W10" # add extra column 'type' to dataframe and assigned 'kelp' label

total_data <- rbind(p_RK4, Mean_Kfloat_H100_W00, Mean_KFloat_H095_W05, Mean_KFloat_H090_W10, Mean_KFloat_H085_W15)

@@

@@

@@

library(ggpubr)
ggarrange(heatmap_RK4, heatmap_Mean_Kfloat_H100_W00, heatmap_Mean_KFloat_H095_W05, heatmap_Mean_KFloat_H090_W10, heatmap_Mean_KFloat_H085_W15, labels = c("A","B","C","D", "E"), common.legend = TRUE, legend = c("right"), ncol = 2, nrow = 3)

>>>>

Min_Kfloat_H100_W00 <- tidync("OceanParcels/trajectory_data/Min_KFloat_H100_W00.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

Min_Kfloat_H100_W00$type <- "Min_Kfloat_H100_W00" # add extra column 'type' to dataframe and assigned 'kelp' label

Min_Kfloat_H095_W05 <- tidync("OceanParcels/trajectory_data/Min_KFloat_H095_W05.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

Min_Kfloat_H095_W05$type <- "Min_Kfloat_H095_W05" # add extra column 'type' to dataframe and assigned 'kelp' label

Min_Kfloat_H090_W10 <- tidync("OceanParcels/trajectory_data/Min_KFloat_H090_W10.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

Min_Kfloat_H090_W10$type <- "Min_Kfloat_H090_W10" # add extra column 'type' to dataframe and assigned 'kelp' label

Min_Kfloat_H085_W15 <- tidync("OceanParcels/trajectory_data/Min_KFloat_H085_W15.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

Min_Kfloat_H085_W15$type <- "Min_Kfloat_H085_W15" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Mean_KFloat_H085_W15$type <- "Mean_KFloat_H085_W15" # add extra column 'type' to dataframe and assigned 'kelp' label

Max_Kfloat_H100_W00 <- tidync("OceanParcels/trajectory_data/Max_KFloat_H100_W00.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

Max_Kfloat_H100_W00$type <- "Max_KFloat_H100_W00" # add extra column 'type' to dataframe and assigned 'kelp' label

Max_Kfloat_H095_W05 <- tidync("OceanParcels/trajectory_data/Max_KFloat_H095_W05.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

Max_Kfloat_H095_W05$type <- "Max_KFloat_H095_W05" # add extra column 'type' to dataframe and assigned 'kelp' label

Max_Kfloat_H090_W10 <- tidync("OceanParcels/trajectory_data/Max_KFloat_H090_W10.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

Max_Kfloat_H090_W10$type <- "Max_KFloat_H090_W10" # add extra column 'type' to dataframe and assigned 'kelp' label

Max_Kfloat_H085_W15 <- tidync("OceanParcels/trajectory_data/Max_KFloat_H085_W15.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

Max_Kfloat_H085_W15$type <- "Max_KFloat_H085_W15" # add extra column 'type' to dataframe and assigned 'kelp' label

total_data <- rbind(p_RK4, Min_Kfloat_H100_W00 , Min_Kfloat_H095_W05, Min_Kfloat_H090_W10, Min_Kfloat_H085_W15, Mean_Kfloat_H100_W00, Mean_KFloat_H095_W05, Mean_KFloat_H090_W10, Mean_KFloat_H085_W15, Max_Kfloat_H100_W00, Max_Kfloat_H095_W05, Max_Kfloat_H090_W10, Max_Kfloat_H085_W15)

@@

heatmap_Min_Kfloat_H100_W00 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H100_W00, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Min_Kfloat_H095_W05 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H095_W05, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Min_Kfloat_H090_W10 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H090_W10, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Min_Kfloat_H085_W15 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H085_W15, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

@@

heatmap_Max_KFloat_H100_W00 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H100_W00, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Max_KFloat_H095_W05 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H095_W05, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Max_KFloat_H090_W10 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H090_W10, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Max_KFloat_H085_W15 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H085_W15, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

@@

library(ggpubr)
ggarrange(heatmap_Min_Kfloat_H100_W00, heatmap_Min_Kfloat_H095_W05,heatmap_Min_Kfloat_H090_W10,heatmap_Min_Kfloat_H085_W15, heatmap_Mean_Kfloat_H100_W00, heatmap_Mean_KFloat_H095_W05, heatmap_Mean_KFloat_H090_W10, heatmap_Mean_KFloat_H085_W15, heatmap_Max_KFloat_H100_W00,heatmap_Max_KFloat_H095_W05, heatmap_Max_KFloat_H090_W10, heatmap_Max_KFloat_H085_W15 , labels = c("AUTO"), common.legend = TRUE, legend = c("right"))
